Fusion Moves for Correlation Clustering

### 2014-11-14 paper/datasets.tex
fixed some still missing stuff from fred
changes thorsten und joerg

%!TEX root = ./egpaper_for_review.tex
\subsection{Datasets}\label{sec:datasets}
\textbf{Social Networks.}\label{sec:nets}
One important application for large scale correlation clustering are social networks.
We consider two of those networks from the Stanford Large Network Dataset Collection\footnote{\url{http://snap.stanford.edu/data/index.html}}.
Both networks are given by weighted directed graphs with edge weights $-1$ and $1$. 
%
The first network is called \emph{Epinions}. 
This is who-trust-whom online social network of a a general consumer review site. 
Each directed edge $a\to b$ indicates that user $a$ trusts  or does not trust user $b$ by a  positive or negative edge-weight, respectively.
The network contains $131828$ nodes and $841372$ edges from which $85.3\%$ are positively weighted.
%
The second network is called \emph{Slashdot}. 
Slashdot is a technology-related news website known for its specific user community. 
In 2002 Slashdot introduced the Slashdot Zoo feature which allows users to tag each other as friend or foe. 
The network was obtained in November 2008 and contains $77350$ nodes and $516575$ edges of which $76.73\%$ are positively weighted.

We consider the problem to cluster this graphs such that positively weighted edges ($E^+_{\to}$) link inside and negatively weighted edges ($E^-_{\to}$) between clusters.
In other words friends and people who trust each other should be in the same segment and foes and non-trusting people in different clusters.
% 
To compensate the high impact of nodes with high degree we can normalize the edge weights such that each person has the same impact on the overall network, by enforcing.
\begin{align}
  \sum_{i\to j \in E_{\to}} |w_{i\to j}| &= 1&\forall i\in V, deg^{\textrm{out}}(i)\geq 1 
\end{align}
We define the following energy function
\begin{align}
 J(y) &= \sum_{i\to j \in E^+_{\to}} y_{ij}\cdot w_{i \to j} +  \sum_{i\to j \in E^-_{\to}} (y_{ij}-1)\cdot w_{i \to j} \nonumber\\
      &= \sum_{ij \in E} y_{ij}\cdot \underbrace{(w_{i \to j}+w_{j \to i})}_{w_{ij}} + \textrm{const}
\end{align}
which is zero if the given partitioning does not violated any relation and larger otherwise.
We name these two datasets \emph{social nets} and \emph{normalized social nets}.

>>>>

%!TEX root = ./egpaper_for_review.tex
\subsection{Datasets}\label{sec:datasets}
\textbf{Social Networks.}\label{sec:nets}
One important application for large scale correlation clustering are social networks.
We consider two of those networks from the Stanford Large Network Dataset Collection\footnote{\url{http://snap.stanford.edu/data/index.html}}.
Both networks are given by weighted directed graphs with edge weights $-1$ and $1$. 
%
The first network is called \emph{Epinions}. 
This is a who-trust-whom online social network of a a general consumer review site. 
Each directed edge $a\to b$ indicates that user $a$ trusts  or does not trust user $b$ by a  positive or negative edge-weight, respectively.
The network contains $131828$ nodes and $841372$ edges from which $85.3\%$ are positively weighted.
%
The second network is called \emph{Slashdot}. 
Slashdot is a technology-related news website known for its specific user community. 
In 2002 Slashdot introduced the Slashdot Zoo feature which allows users to tag each other as friend or foe. 
The network was obtained in November 2008 and contains $77350$ nodes and $516575$ edges of which $76.73\%$ are positively weighted.

We consider the problem to cluster this graphs such that positively weighted edges ($E^+_{\to}$) link inside and negatively weighted edges ($E^-_{\to}$) between clusters.
In other words friends and people who trust each other should be in the same segment and foes and non-trusting people in different clusters.
% 
To compensate the high impact of nodes with high degree we can normalize the edge weights such that each person has the same impact on the overall network, by enforcing.
\begin{align}
  \sum_{i\to j \in E_{\to}} |w_{i\to j}| &= 1&\forall i\in V, deg^{\textrm{out}}(i)\geq 1 
\end{align}
We define the following energy function
\begin{align}
 J(y) &= \sum_{i\to j \in E^+_{\to}} y_{ij}\cdot w_{i \to j} +  \sum_{i\to j \in E^-_{\to}} (y_{ij}-1)\cdot w_{i \to j} \nonumber\\
      &= \sum_{ij \in E} y_{ij}\cdot \underbrace{(w_{i \to j}+w_{j \to i})}_{w_{ij}} + \textrm{const}
\end{align}
which is zero if the given partitioning does not violates any relation and larger otherwise.
We name these two datasets \emph{social nets} and \emph{normalized social nets}.

### 2014-11-14 paper/egpaper_for_review.tex
fixed some still missing stuff from fred
changes thorsten und joerg

But EHC is very fast, and can be used to initialize
CGC~\cite{beier_2014_cvpr}. Excessive time in CGC
is spend in the \emph{cut phase} to solve the 
first two coloring on the complete graph.
As shown in Sec.~\ref{sec:exp},
allowing CGC to start from the EHC solution
can improve performance drastically.

@@

As classical fusion, CC-Fusion does not provide a lower bound on the objective and 
has no sound stopping condition.
For latter we use a maximal number of iterations and maximal number of iteration without improvement as stopping condition.

@@

\subsection{Fast Optimization of CC-Fusion Moves} \label{sec:fast_optimization}
In general the auxiliary fusion problem~\ref{eq:fusion_move_a} is, as for classical fusion~\cite{Lempitsky-2010}, NP-hard.
However, many variables have been fixed to be zero and we can reformulate~\ref{eq:fusion_move_a}
into a correlation clustering problem on a coarser graph, where all nodes which are connected
via must-link constraints are merged into single nodes. We call this graph \emph{contracted graph}.
%
\begin{definition}\emph{(Contracted Graph)}
Given a weighted graph $G=(V,E,w)$ and a segmentation of $G$ given by $y\in P(G)$,
we define the contraction of graph $G_y=(V_y,E_y, \bar{w})$
by $V_y=\{l_v(y)|v\in V\}$, $E_y=\{l_u(y)l_v(y)|uv\in E\}$, and 
$\forall \bar{u}\bar{v}\in E_y: \bar{w}_{\bar{u}\bar{v}}=\sum_{uv\in E, l_u(y)=\bar{u},l_v(y)=\bar{v}}w_{uv}$ 
\end{definition}
%
Any clustering $\bar{y}$ of the contracted graph $G_y=(V_y,E_y)$ can be \emph{back projected} to a clustering $\tilde{y}$ the original graph $G=(V,E)$ by
%
\begin{align}
\tilde{y}_{uv}&=\left\{ 
\begin{array}{ll}
\bar{y}_{l_u(y)l_v(y)}& \textrm{ if }l_u(y) \neq l_v(y)\\
0                & \textrm{ else}
\end{array}
\right.& \forall uv \in E
\end{align}

@@

\begin{theorem}[Equivalence]\label{thm:Equivalence}
The back projection of the optimal segmentation $\bar{y}'$ of the contracted graph $G_y=(V_y,E_y, \bar{w})$
is an optimal solution of problem~\ref{eq:fusion_move_a}.
\begin{proof}
Let $y'$ be the back propagation of $\bar{y}'$, which is by definition feasible for~\ref{eq:fusion_move_a}.
If $y'$ would not be an optimal solution there must be a $y''$ with 
$\sum_{e\in E} w_ey_e' > \sum_{e\in E} w_ey_e''$.
Since $y_e'$ and $y_e''$ are $0$ for all $e \in \mathcal{E}_0^{\breve{y}}$ we would have
\begin{align*}
  \sum_{\bar{e}\in E_y} \bar{w}_{\bar{e}}\bar{y}'_{\bar{e}}
 &= \sum_{e\in E \setminus \mathcal{E}_0^{\breve{y}}} w_ey_e'          
  = \sum_{e\in E} w_ey_e' \\
 &> \sum_{e\in E} w_ey_e''
  = \sum_{e\in E \setminus \mathcal{E}_0^{\breve{y}}} w_ey_e''
  =\sum_{\bar{e}\in E_y} \bar{w}_{\bar{e}}\bar{y}''_{\bar{e}}
\end{align*}
where $\bar{y}''$ is the projection from $y''$ on $G_y$.
This contradicts that $y'$ is a optimal segmentation of $G_y$.
\end{proof}
%
\end{theorem}

@@

\begin{figure}
\centering
\input{polytope-tikz.tex}
\caption{Each move can be interpreted as an optimization of an inner polytope.
Each inner polytope includes the current vertex. Starting with $y_0$ we optimize over the red polytope 
and find $y_1$ as optima. When optimize over the blue polytope we stay in $y_1$ as optima.
When optimizing over the green polytope we find $y_2$ which we will never leave again or any polytope containing~$y_2$. 
}
\label{fig:polyheadral}
\end{figure}

@@

    \end{semilogxaxis}
    \end{tikzpicture}
  \begin{center}
  \hypersetup{linkcolor = black}
  \ref{ledgendPositionMC}
  \hypersetup{linkcolor = red}
  \end{center}
    \caption{Comparison of the Multicut implementation of OpenGM and 
    our modified implementation, which can deal better with large scale problems. 
    However, for large scale problems it still does not scale.}
    \label{fig:at:knott-450b}
  \end{figure}

\subsection{Parameter Choice for CC-Fusion}
Beside the choice of the proposal generator and fusion method CC-Fusion has some more parameters, which need to be set.
The most crucial one is the number of segments in the proposal. For HC we also have to set the noise which is used to generate diversity.
Fig.~\ref{fig:parameterchoice} shows an evaluation of the impact of this parameters for a single instance of knott-3d-450 averaged over several random seeds.
The runtime depends on the number of clusters in the proposal (Fig.~\ref{fig:parameterchoice} left), which controls the size of the auxiliary move problems.
The level of noise has no major impact on the runtime.
The energy of the final solution improves with finer proposals since this increases the search space of the moves.
The level of noise has to be large enough to generate diverse proposals but not to large to generate proposals with low quality.
As shown in Fig.~\ref{fig:parameterchoice} right the useful parameter set is quite large. This allows us to use the same parameters for \emph{all}
experiments. However we would like to note, that in practice we can improve the performance by adjusting these parameters for the specific problem setting.
%
%
\begin{figure}[th]
\centering
\fbox{\includegraphics[width=0.45\columnwidth,trim=3.5cm 8cm 4.5cm 8cm,clip]{images/grid-time2.pdf}}
\fbox{\includegraphics[width=0.45\columnwidth,trim=3.5cm 8cm 4.5cm 8cm,clip]{images/grid-value2.pdf}}
\caption{Empirical evaluation of the impact of noise used for proposal generation and proposal size.
  Proposals with many segments cause longer runtime. Noise seemed not to be a critical parameter but should be selected large enough.
}
\label{fig:parameterchoice}
\end{figure}

@@

\begin{table}[t]
   \tiny
   \centering
   \caption{Evaluation by Variation of Information (VOI) Rand Index (RI) for datasets with available ground-truth.}
   \label{tab:eval}
   \begin{tabular}{lllllll}
      \toprule
         VOI              &  image-seg   & knott-3d-150 & knott-3d-300   & knott-3d-450 & knott-3d-550 &3d-seg\\
      \midrule 
         PIVOT-BOEM       &\rd$ 4.9633$  &\rd $ 2.9936$ &\rd $ 4.4986$   &      --      &    --        &  --\\ 
         HC               &   $ 2.5967$  &    $ 1.5477$ &    $ 2.3513$   &    $ 2.9155$ &    --        & $       2.8395$\\
         HC-CGC           &   $ 2.5164$  &    $ 0.9052$ &    $ 1.7636$   &    $ 2.2256$ &    --        & $       1.7603$ \\
         CGC              &   $ 2.5247$  &    $ 0.9267$ &    $ 1.8822$   &    $ 2.3104$ &    --        & $\rd    6.8908$ \\
         KL               &   $ 2.6432$  &\rd $ 2.0648$ &\rd $ 4.1318$   &\rd $ 4.9270$ &    --        & $\rd    7.1057$\\
         FUSION           &$\bf 2.1406$  &\rd $ 2.8787$ &\rd $ 4.0744$   &\rd $ 4.6616$ &    --        & $\rd    6.5366$ \\
         MC-R             &   $ 2.5471$  &    $ 0.9178$ &    $ 1.6369$   &    $ 2.8710$ &    --        & $\rd    6.5058$\\   
         MC-I             &   $ 2.5367$  & $\bf 0.9063$ & $\bf 1.6352$   & $\bf 2.0037$ &    --        & $\rd    4.3319$\\  
         CC-Fusion-HC-MC   &   $ 2.5319$  &    $ 0.9629$ &    $ 1.6516$   &    $ 2.0801$ &    --        & $\bf    1.3347$ \\  
         CC-Fusion-HC-CGC  &$\bf 2.4961$  &    $ 0.9679$ &    $ 1.7673$   &    $ 2.3809$ &    --        & $       2.1347$ \\  
         CC-Fusion-WS-MC   &   $ 2.5340$  &    $ 0.9629$ &    $ 1.6742$   &    $ 2.0739$ &    --        & $\bf    1.3334$ \\  
         CC-Fusion-WS-CGC  &   $ 2.5192$  &    $ 1.0585$ &    $ 2.1344$   &    $ 2.7487$ &    --        & $       3.3514$ \\      
      \bottomrule
   \end{tabular}

   \begin{tabular}{lllllll}
      \toprule
          RI              &  image-seg   & knott-3d-150 & knott-3d-300   & knott-3d-450 & knott-3d-550 &3d-seg\\
      \midrule 
         PIVOT-BOEM       &   $ 0.7438$  &\rd $ 0.7851$ &    $  0.8792$  &      --      &    --        &  --\\ 
         HC               &   $ 0.7560$  &\rd $ 0.8139$ &\rd $  0.8084$  &\rd $ 0.7610$ &    --        &   $ 0.9651$\\
         HC-CGC           &   $ 0.7724$  &    $ 0.9226$ &    $  0.8713$  &    $ 0.8433$ &    --        &   $ 0.9861$ \\
         CGC              &   $ 0.7590$  &    $ 0.9206$ &    $  0.8666$  &    $ 0.8341$ &    --        &\rd$ 0.6024$ \\
         KL               &\rd$ 0.6400$  &\rd $ 0.8085$ &\rd $  0.6858$  &\rd $ 0.6409$ &    --        &\rd$ 0.5849$\\
         FUSION           &\rd$ 0.5480$  &\rd $ 0.2849$ &\rd $  0.1420$  &\rd $ 0.0998$ &    --        &\rd$ 0.0345$ \\
         MC-R             &   $ 0.7822$  &    $ 0.9232$ & $\bf  0.8849$  &\rd $ 0.6713$ &    --        &\rd$ 0.0432$ \\   
         MC-I             &   $ 0.7821$  & $\bf 0.9236$ & $\bf  0.8849$  & $\bf 0.8670$ &    --        &\rd$ 0.5461$\\  
         CC-Fusion-HC-MC   &   $ 0.7801$  &    $ 0.9042$ &    $  0.8824$  &    $ 0.8573$ &    --        &$\bf 0.9906$ \\  
         CC-Fusion-HC-CGC  &   $ 0.7780$  &    $ 0.9031$ &    $  0.8763$  &    $ 0.8470$ &    --        &   $ 0.9775$ \\  
         CC-Fusion-WS-MC   &$\bf 0.7825$  &    $ 0.9042$ &    $  0.8802$  &    $ 0.8582$ &    --        &   $ 0.8895$ \\  
         CC-Fusion-WS-CGC  &   $ 0.7750$  &    $ 0.8951$ &    $  0.8596$  &    $ 0.8394$ &    --        &   $\bf 0.9906$ \\      
      \bottomrule
   \end{tabular}
\end{table}

@@

We have presented a fast and scalable 
approximate solver for correlation 
clustering, named Correlation Clustering Fusion (CC-Fusion).
It is orthogonal to previous research, \ie it can be combined with
correlation clustering solver.
%
The best solution is iteratively improved 
by a fusion with proposal solutions.
The fusion move itself is formulated as correlation
clustering on a smaller graph with fewer edges and nodes
and can therefore be solved much faster than the original problem.

Our evaluation shows that several CC-Fusion algorithms
outperforms state-of-the-art solvers w.r.t. any time performance 
with increasing problem size.

>>>>

But EHC is very fast, and can be used to initialize
CGC~\cite{beier_2014_cvpr}. Excessive time in CGC
is spent in the \emph{cut phase} to solve the 
first two coloring on the complete graph.
As shown in Sec.~\ref{sec:exp},
allowing CGC to start from the EHC solution
can improve performance drastically.

@@

As classical fusion, CC-Fusion does not provide a lower bound on the objective and 
has no sound stopping condition.
For the latter we use a maximal number of iterations and maximal number of iteration without improvement as stopping condition.

@@

\subsection{Fast Optimization of CC-Fusion Moves} \label{sec:fast_optimization}
In general the auxiliary fusion problem~\ref{eq:fusion_move_a} is, as for classical fusion~\cite{Lempitsky-2010}, NP-hard.
However, many variables have been fixed to be zero and we can reformulate~\ref{eq:fusion_move_a}
into a correlation clustering problem on a coarser graph, where all nodes which are connected
via must-link constraints are merged into single nodes. We call this graph \emph{contracted graph}.
%
\begin{definition}\emph{(Contracted Graph)}
Given a weighted graph $G=(V,E,w)$ and a segmentation of $G$ given by $y\in P(G)$,
we define the contraction of graph $G_y=(V_y,E_y, \bar{w})$
by $V_y=\{l_v(y)|v\in V\}$, $E_y=\{l_u(y)l_v(y)|uv\in E\}$, and 
$\forall \bar{u}\bar{v}\in E_y: \bar{w}_{\bar{u}\bar{v}}=\sum_{uv\in E, l_u(y)=\bar{u},l_v(y)=\bar{v}}w_{uv}$ 
\end{definition}
%
Any clustering $\bar{y}$ of the contracted graph $G_y=(V_y,E_y)$ can be \emph{back projected} to a clustering $\tilde{y}$ of the original graph $G=(V,E)$ by
%
\begin{align}
\tilde{y}_{uv}&=\left\{ 
\begin{array}{ll}
\bar{y}_{l_u(y)l_v(y)}& \textrm{ if }l_u(y) \neq l_v(y)\\
0                & \textrm{ else}
\end{array}
\right.& \forall uv \in E
\end{align}

@@

\begin{theorem}[Equivalence]\label{thm:Equivalence}
The back projection of the optimal segmentation $\bar{y}'$ of the contracted graph $G_y=(V_y,E_y, \bar{w})$
is an optimal solution of problem~\ref{eq:fusion_move_a}.
\begin{proof}
Let $y'$ be the back propagation of $\bar{y}'$, which is by definition feasible for~\ref{eq:fusion_move_a}.
If $y'$ would not be an optimal solution, there must be a $y''$ with 
$\sum_{e\in E} w_ey_e' > \sum_{e\in E} w_ey_e''$.
Since $y_e'$ and $y_e''$ are $0$ for all $e \in \mathcal{E}_0^{\breve{y}}$ we would have
\begin{align*}
  \sum_{\bar{e}\in E_y} \bar{w}_{\bar{e}}\bar{y}'_{\bar{e}}
 &= \sum_{e\in E \setminus \mathcal{E}_0^{\breve{y}}} w_ey_e'          
  = \sum_{e\in E} w_ey_e' \\
 &> \sum_{e\in E} w_ey_e''
  = \sum_{e\in E \setminus \mathcal{E}_0^{\breve{y}}} w_ey_e''
  =\sum_{\bar{e}\in E_y} \bar{w}_{\bar{e}}\bar{y}''_{\bar{e}}
\end{align*}
where $\bar{y}''$ is the projection from $y''$ on $G_y$.
This contradicts that $y'$ is a optimal segmentation of $G_y$.
\end{proof}
%
\end{theorem}

@@

\begin{figure}
\centering
\input{polytope-tikz.tex}
\caption{Each fusion move can be interpreted as an optimization of an inner polytope.
Each inner polytope includes the current vertex. Starting with $y_0$ we optimize over the red polytope 
and find $y_1$ as optima. When optimize over the blue polytope we stay in $y_1$ as optima.
When optimizing over the green polytope we find $y_2$ which we will never leave again or any polytope containing~$y_2$. 
}
\label{fig:polyheadral}
\end{figure}

@@

    \end{semilogxaxis}
    \end{tikzpicture}
  \begin{center}
  \hypersetup{linkcolor = black}
  \ref{ledgendPositionMC}
  \hypersetup{linkcolor = red}
  \end{center}
    \caption{Comparison of the Multicut implementation of OpenGM and 
    our modified implementation, which improves the runtime.
    However, for large scale problems it still does not scale.}
    \label{fig:at:knott-450b}
  \end{figure}

\subsection{Parameter Choice for CC-Fusion}
Beside the choice of the proposal generator and fusion method CC-Fusion has some more parameters, which need to be set.
The most crucial one is the number of segments in the proposal. For HC we also have to set the noise which is used to generate diversity.
Fig.~\ref{fig:parameterchoice} shows an evaluation of the impact of this parameters for a single instance of knott-3d-450 averaged over several random seeds.
The runtime depends on the number of clusters in the proposal (Fig.~\ref{fig:parameterchoice} left), which controls the size of the auxiliary move problems.
The level of noise has no major impact on the runtime.
The energy of the final solution improves with finer proposals since this increases the search space of the moves.
The level of noise has to be large enough to generate diverse proposals, but not too large which would lead to proposals with low quality.
As shown in Fig.~\ref{fig:parameterchoice} right the useful parameter set is quite large. This allows us to use the same parameters for \emph{all}
experiments. However we would like to note that in practice we can improve the performance by adjusting these parameters for the specific problem setting.
%
%
\begin{figure}[th]
\centering
\fbox{\includegraphics[width=0.45\columnwidth,trim=3.5cm 8cm 4.5cm 8cm,clip]{images/grid-time2.pdf}}
\fbox{\includegraphics[width=0.45\columnwidth,trim=3.5cm 8cm 4.5cm 8cm,clip]{images/grid-value2.pdf}}
\caption{Empirical evaluation of the impact of noise used for proposal generation and proposal size.
  Proposals with many segments cause longer runtime. Noise seemed not to be a critical parameter but should be selected large enough.
}
\label{fig:parameterchoice}
\end{figure}

@@

\begin{table}[t]
   \tiny
   \centering
   \caption{Evaluation by Variation of Information (VOI) and Rand Index (RI) for datasets with available ground truth.}
   \label{tab:eval}
   \begin{tabular}{llllll}
      \toprule
         VOI              &  image-seg   & knott-3d-150 & knott-3d-300   & knott-3d-450 &3d-seg\\
      \midrule 
         PIVOT-BOEM       &\rd$ 4.9633$  &\rd $ 2.9936$ &\rd $ 4.4986$   &      --       &  --\\ 
         HC               &   $ 2.5967$  &    $ 1.5477$ &    $ 2.3513$   &    $ 2.9155$  & $       2.8395$\\
         HC-CGC           &   $ 2.5164$  &    $ 0.9052$ &    $ 1.7636$   &    $ 2.2256$  & $       1.7603$ \\
         CGC              &   $ 2.5247$  &    $ 0.9267$ &    $ 1.8822$   &    $ 2.3104$  & $\rd    6.8908$ \\
         KL               &   $ 2.6432$  &\rd $ 2.0648$ &\rd $ 4.1318$   &\rd $ 4.9270$  & $\rd    7.1057$\\
         FUSION           &$\bf 2.1406$  &\rd $ 2.8787$ &\rd $ 4.0744$   &\rd $ 4.6616$  & $\rd    6.5366$ \\
         MC-R             &   $ 2.5471$  &    $ 0.9178$ &    $ 1.6369$   &    $ 2.8710$  & $\rd    6.5058$\\   
         MC-I             &   $ 2.5367$  & $\bf 0.9063$ & $\bf 1.6352$   & $\bf 2.0037$  & $\rd    4.3319$\\  
         CC-Fusion-HC-MC   &   $ 2.5319$  &    $ 0.9629$ &    $ 1.6516$   &    $ 2.0801$ & $\bf    1.3347$ \\  
         CC-Fusion-HC-CGC  &$\bf 2.4961$  &    $ 0.9679$ &    $ 1.7673$   &    $ 2.3809$ & $       2.1347$ \\  
         CC-Fusion-WS-MC   &   $ 2.5340$  &    $ 0.9629$ &    $ 1.6742$   &    $ 2.0739$ & $\bf    1.3334$ \\  
         CC-Fusion-WS-CGC  &   $ 2.5192$  &    $ 1.0585$ &    $ 2.1344$   &    $ 2.7487$ & $       3.3514$ \\      
      \bottomrule
   \end{tabular}

   \begin{tabular}{llllll}
      \toprule
          RI              &  image-seg   & knott-3d-150 & knott-3d-300   & knott-3d-450  &3d-seg\\
      \midrule 
         PIVOT-BOEM       &   $ 0.7438$  &\rd $ 0.7851$ &    $  0.8792$  &      --       &  --\\ 
         HC               &   $ 0.7560$  &\rd $ 0.8139$ &\rd $  0.8084$  &\rd $ 0.7610$  &   $ 0.9651$\\
         HC-CGC           &   $ 0.7724$  &    $ 0.9226$ &    $  0.8713$  &    $ 0.8433$  &   $ 0.9861$ \\
         CGC              &   $ 0.7590$  &    $ 0.9206$ &    $  0.8666$  &    $ 0.8341$  &\rd$ 0.6024$ \\
         KL               &\rd$ 0.6400$  &\rd $ 0.8085$ &\rd $  0.6858$  &\rd $ 0.6409$  &\rd$ 0.5849$\\
         FUSION           &\rd$ 0.5480$  &\rd $ 0.2849$ &\rd $  0.1420$  &\rd $ 0.0998$  &\rd$ 0.0345$ \\
         MC-R             &   $ 0.7822$  &    $ 0.9232$ & $\bf  0.8849$  &\rd $ 0.6713$  &\rd$ 0.0432$ \\   
         MC-I             &   $ 0.7821$  & $\bf 0.9236$ & $\bf  0.8849$  & $\bf 0.8670$  &\rd$ 0.5461$\\  
         CC-Fusion-HC-MC   &   $ 0.7801$  &    $ 0.9042$ &    $  0.8824$  &    $ 0.8573$ &$\bf 0.9906$ \\  
         CC-Fusion-HC-CGC  &   $ 0.7780$  &    $ 0.9031$ &    $  0.8763$  &    $ 0.8470$ &   $ 0.9775$ \\  
         CC-Fusion-WS-MC   &$\bf 0.7825$  &    $ 0.9042$ &    $  0.8802$  &    $ 0.8582$ &   $ 0.8895$ \\  
         CC-Fusion-WS-CGC  &   $ 0.7750$  &    $ 0.8951$ &    $  0.8596$  &    $ 0.8394$ &   $\bf 0.9906$ \\      
      \bottomrule
   \end{tabular}
\end{table}

@@

We have presented a fast and scalable 
approximate solver for correlation 
clustering, named Correlation Clustering Fusion (CC-Fusion).
It is orthogonal to previous research, \ie it can be combined with
correlation clustering solver.
%
The best solution is iteratively improved 
by a fusion with proposal solutions.
The fusion move itself is formulated as correlation
clustering on a smaller graph with fewer edges and nodes
and can therefore be solved much faster than the original problem.
%
Our evaluation shows that several CC-Fusion algorithms
outperform state-of-the-art solvers w.r.t. any time performance 
with increasing problem size.

\enlargethispage{0.4cm}

### 2014-11-14 paper/evaluation.tex
fixed all changes where i knew the fix to
changes thorsten und joerg

%!TEX root = ./egpaper_for_review.tex
\subsection{Evaluation}
For the evaluation of the different methods on the datasets introduced in Sec.~\ref{sec:datasets},
we show zoomed anytime plots in  Fig.~\ref{fig:anytime} and variation of information (VOI)~\cite{meila-2003}
and rand index (RI)~\cite{rand-1971} of the final solutions in Tab.~\ref{tab:eval}.
Anytime plots with no zooming and a detailed evaluation are given in supplementary material.

For \emph{social-nets} CC-Fusion methods provide the best results for the first minutes .
Only CGC and HC-CGC are able to find better solutions after more than 1000 seconds.
MC-I and MC-R can not be applied to such large problems.
We belief that with better proposal generators, which are more suited for such network problems,
we can improve CCFusion. One candidate for such a generator would be a scalable implementation of the 
PIVOT algorithm.

For \emph{modularity-clustering} CC-Fusion performs on par to competitive methods, even CC-Fusion 
and the used parameters have not been designed and chosen for this type of problem.
Especially it does a better job than MC-I.

For \emph{image-seg} CC-Fusion is faster than other methods and competitive in terms of energy, VOI, and RI.
Because  the models are designed to have a high boundary recall (oversegmentation), 
classical fusion, which return undersegmentations, is best best VOI but worse RI and energy.
Proposals generated by EHC seemed to be a bit better than WS-based ones.

For the \emph{knott-datasets} similar holds as for image-seg. 
With increasing problem size CC-Fusion-HC-MC and CC-Fusion-WS-MC have a better performance compared to competitive methods, \cf Fig.~\ref{fig:anytime}(b-e).
Also in terms of VOI and RI they are only slightly worse than the globally optimal solution found by MC-I.
The initialization of CGC by HC denoted by HC-CGC also improves the performance compared to native CGC.
For the largest 3D volume seg-3d, HC-CGC gives the first useful solution, \cf  Fig.~\ref{fig:anytime}(f).
However, after a few minutes  CC-Fusion-HC-MC and CC-Fusion-WS-MC give much better results and also overall best in terms of energy, VOI, and RI.
%
Pure EHC, Fusion and PIVOT-BOEM do not give useful results on any dataset.

>>>>

%!TEX root = ./egpaper_for_review.tex
\subsection{Evaluation}
For the evaluation of the different methods on the datasets introduced in Sec.~\ref{sec:datasets},
we show zoomed anytime plots in  Fig.~\ref{fig:anytime} and variation of information (VOI)~\cite{meila-2003}
and rand index (RI)~\cite{rand-1971} of the final solutions in Tab.~\ref{tab:eval}.
Anytime plots with no zooming and a detailed evaluation are given in supplementary material. 
%
For \emph{social-nets} CC-Fusion methods provide the best results for the first minutes .
Only CGC and HC-CGC are able to find better solutions after more than 1000 seconds.
MC-I and MC-R can not be applied to such large problems.
We belief that with better proposal generators, which are more suited for such network problems,
we can improve CCFusion. One candidate for such a generator would be a scalable implementation of the 
PIVOT algorithm.
%
For \emph{modularity-clustering} CC-Fusion performs on par to competitive methods, even CC-Fusion 
and the used parameters have not been designed and chosen for this type of problem.
Especially it does a better job than MC-I.
%
For \emph{image-seg} CC-Fusion is faster than other methods and competitive in terms of energy, VOI, and RI.
Because  the models are designed to have a high boundary recall (oversegmentation), 
classical fusion, which return undersegmentations, is best best VOI but worse RI and energy.
Proposals generated by EHC seemed to be a bit better than WS-based ones.
%
For the \emph{knott-datasets}
with increasing problem size CC-Fusion-HC-MC and CC-Fusion-WS-MC have a better performance compared to competitive methods, \cf Fig.~\ref{fig:anytime}(b-e).
Also in terms of VOI and RI they are only slightly worse than the globally optimal solution found by MC-I.
The initialization of CGC by HC denoted by HC-CGC also improves the performance compared to native CGC.
For the largest 3D volume seg-3d, HC-CGC gives the first useful solution, \cf  Fig.~\ref{fig:anytime}(f).
However, after a few minutes  CC-Fusion-HC-MC and CC-Fusion-WS-MC give much better results and also overall best in terms of energy, VOI, and RI.
%
Pure EHC, Fusion and PIVOT-BOEM do not give useful results on any dataset.
